% \documentclass{report}

% \usepackage{subcaption} % package for subfigures
% \usepackage{hyperref}  % package for linking figures etc
% \usepackage{enumitem}  % package for description with bullets
% \usepackage{graphicx}  % package for importing images
% \usepackage{mathtools} % package for math equation
% \usepackage{mathrsfs}  % package for math font
% \usepackage{indentfirst} % package for getting ident after section or paragraph
% \usepackage[export]{adjustbox}
% \usepackage{multirow}  % package for tables, multir
% \usepackage{amssymb}
% % \usepackage{tabu}   % for tables 
% \setlength{\parindent}{2em} % how much indent to use when we start a paragraph

% \graphicspath{ {./theory/figures/} }       % path for images

% \begin{document}

\chapter{Conclusion - Future work}

\section{Conclusion}
In this thesis, we explored the problem of action recognition and localization. We design a network based on the approach proposed by \cite{DBLP:journals/corr/HouCS17}
combined with some elements presented by \cite{DBLP:journals/corr/abs-1712-09184}, \cite{Ren:2015:FRT:2969239.2969250}, \cite{Girshick:2015:FR:2919332.2920125},
\cite{DBLP:journals/corr/abs-1903-00304} and \cite{hara3dcnns}. \par

We wrote a pytorch implementation, expanding code only from \cite{jjfaster2rcnn}. Furthermore, we wrote our own code using some CUDA functions designed by us (like
calculating connection scores, modifying tubes etc). \par

We tried to  a design the  Tube Proposal Network for proposing ToIs in given video segments, inspired by Faster R-CNN's RPN.
We designed it using general anchors and not dataset specific anchors. This means that we try to generalize our approach for several datasets, on the contrary with
the approach proposed by \cite{DBLP:journals/corr/abs-1712-09184}, in which it uses the most frequently appearing anchors for each dataset.

On top of that, we designed a naive connection algorithm for connecting  proposed ToIs based on the algorithm proposed by \cite{DBLP:journals/corr/abs-1712-09184}.
In our approach, we use the same scoring policy, which is a combination between actioness and overlapping scores. The main difference is that we avoid to calculate
all the possible combinations using an updatable threshold. We, also, tried another connection algorithm inspired by \cite{DBLP:journals/corr/abs-1903-00304}. However,
our implementation wasn't very good so, we didn't explore all of its potentials. \par

Finally, we explored several classifiers for the classification stage of our network, which are a RNN, an SVM and an MLP.  We used an implementation taken from Fast RCNN
for the SVM classifier, which included hard negatives mining training procedure. We explored some training techniques for best classification performance and
2 training approaches for MLP classifier, the classic one and using pre-extracted features. 

\section{Future work}
There is a lot of room for improvement for our network, in order to achieve state-of-the-art results. The most important are described in the next paragraphs.

\paragraph{Improving TPN proposals} We implemented 2 networks for proposing action tubes in a video segment. We managed to achieve about 63\% recall score for
sample duration = 16 and about 80\% recall for sample duration = 8. Theses scores show that there is plenty room for improvement, especially for sample duration = 16.
Even though a lot of networks' architectures have been explored for regression, a good idea would be to try other networks, not necessarily inspired by object detection
networks like we did. On top of that, adding a $\lambda$ factor in training loss would be a good idea and exploring which is the best approach.
So training loss could be defined as:
\begin{equation} 
\begin{split}
 L  =  \sum_iL_{cls}(p_i, p_i^*) + \lambda_1 \sum_ip_i^*L_{reg}(t_i,t_i^*) + \lambda_2  \sum_iq_i^*L_{reg}(c_{i}, c_{i}^*) \\
\end{split}
\end{equation}

Furthermore, it would be a good idea to use SSD's (\cite{DBLP:journals/corr/LiuAESR15}) proposal network instead of RPN, in order to compare result. Finally,
we could experiment using Feature Pyramid Networks(\cite{8099589}), which could be exteded in 3 dimensions as another feature extractor or some other type of 3D ResNet.

\paragraph{Changing Connection algorithm}
In this thesis, another challenge we came was connecting proposed ToIs for proposing action tubes. We implemented a very naive algorithm, which wasn't
able to give us very good proposals despite the changes we tried to do. We implemented another connection algorithm which was based on estimationing temporal
progress of an action tube  and its overlap with others. Although it also didn't give us very good proposals, we believe that we should explore this algorithm's potential. That's
because it takes advantage of the progress of the action, which the previous algorithm didn't.

\paragraph{Explore other  classification techniques}
For classification stage, we experimented mainly on an SVM classifier for JHMDB dataset and we didn't get involved with UCF dataset. Our first
goal is to be able to get good classification results for UCF dataset, too.  We think that we should explore UCF's feature maps and techniques applied at feature maps before  classification. In addition, we could try other classification techniques like random forest or experiment more with RNN classifier for the UCF dataset.
Finally, another classification procedure would be a good idea, like extracting first all the possible action tubes and then using other network's features for classification
stage.

% \end{document}
