\documentclass[diploma]{softlab-thesis}


%%%
%%%  The document
%%%

\usepackage{hyperref}  % package for linking figures etc
\usepackage{enumitem}  % package for description with bullets
\usepackage{graphicx}  % package for importing images
\usepackage{mathtools} % package for math equation
\usepackage{mathrsfs}  % package for math font
\usepackage{indentfirst} % package for getting ident after section or paragraph
\usepackage{subcaption} % package for subfigures
\usepackage[export]{adjustbox}
\usepackage{longtable} % package for multi pages tables
\usepackage{multirow}  % package for tables, multirow

% \usepackage{amsmath}
\usepackage[
    backend=bibtex,
    style=authoryear,
    sorting=ynt,
    % style=numeric,
    % style=alphabetic ,
  ]{biblatex}
 \addbibresource{References}

\graphicspath{ {./theory/figures/} }       % path for images
\begin{document}

%%%  Title page

\frontmatter

\title{Action Localization and Recognition in Videos}
\author{Efstatios Galanakis}
\date{July 2019}
\datedefense{-1}{12}{2019}

\supervisor{}
\supervisorpos{}

\committeeone{}
\committeeonepos{}
\committeetwo{}
\committeetwopos{}
\committeethree{}
\committeethreepos{}

\TRnumber{CSD-SW-TR-42-14}  % number-year, ask nickie for the number
\department{}

\maketitle


%%%  Abstract, in English

\begin{abstracten}%
  The purpose of this diploma thesis is the design of a simple
  network for recognizing and localition human actions in videos.
  This network produces a sequence of 2D boxes for each video and
  a classification label for each action. 

  The need for ...

  
  The purpose of this diploma dissertation is on one hand the design
  of a simple high-level language that supports programming with
  proofs, and on the other hand the implementation of a compiler for
  this language. This compiler will produce code for an
  intermediate-level language suitable for creating certified
  binaries.

  The need for reliable and certifiably secure code is even more
  pressing today than it was in the past. In many cases, security and
  software compatibility issues put in danger the operation of large
  systems, with substantial financial consequences. The lack of a
  formal way of specifying and proving the correctness of programs that
  characterizes current programming languages is one of the main reasons
  why these issues exist. In order to address this problem, a number of
  frameworks with support for certified binaries have recently been
  proposed. These frameworks offer the possibility of specifying and
  providing a formal proof of the correctness of programs. Such a proof
  can easily be checked for validity before running the program.

  The frameworks that have been proposed are intermediate-level in
  nature, thus the process of programming in these is rather cumbersome.
  The high-level languages that accompany some of these frameworks,
  while very expressive, are hard to use. A simpler high-level language,
  like the one proposed in this dissertation, would enable further use
  of this programming idiom.

  In the language we propose, the programmer specifies the partial
  correctness of a program by annotating function definitions with pre-
  and post-conditions that must hold for their parameters and results.
  The programmer also provides a set of theorems, based on which proofs
  of the proper implementation and use of the functions are constructed.
  An implementation in OCaml of a compiler from this language to the
  NFLINT certified binaries framework was also completed as part of this
  dissertation.

  We managed to keep the language close to the feel of the current
  widespread functional languages, and also to fully separate the
  programming stage from the correctness-proving stage. Thus an average
  programmer can program in a familiar way in our language, and later an
  expert on formal logic can prove the semi-correctness of a program.
  As evidence of the practicality of our design, we provide a number of
  examples in our language with full semi-correctness proofs.
\begin{keywordsen}
Programming languages, Programming with proofs, Secure programming
languages, Certified code.
\end{keywordsen}
\end{abstracten}


%%%  Acknowledgements

% \begin{acknowledgementsgr}
% \end{acknowledgementsgr}


%%%  Various tables

\tableofcontents
\listoftables
\listoffigures


%%%  Main part of the book

\mainmatter

\include{chapter1}
\include{chapter2}
\include{chapter3}
\include{chapter4}
\include{chapter5}
\include{chapter6}
\include{chapter7}
%%%  Bibliography

% \bibliographystyle{softlab-thesis}
% \bibliography{References}
%%% mine
\printbibliography

% %%%  Appendices

% \backmatter

% \appendix

% \chapter{}

% $A \rightarrow B$ : συνάρτηση από το πεδίο $A$ στο πεδίο $B$.

% \chapter{}

% \textbf{Haskell} : η γλώσσα της ζωής μου.

% \chapter{}

% 42 : life, the universe and everything.


%%%  End of document

\end{document}
